Mistriage

### 2019-05-29 ManuscriptMarkdown.Rmd
Add files via upload

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
## LOADING ENVIROMENT AND TABLES
## Original results and UI tables
results <- readRDS("output/original.results.Rds")
result.tables <- readRDS("result.tables.Rds")
result.tables.data.frame <- readRDS("result.tables.data.frame.Rds")
## Sample characteristics table
# table.one <-

## PREPARED CODE
## Total patients and NA
total.number.of.patients <- nrow(results$data.sets.before.imputations$multi.centre.vs.single.centre$multi.centre)
total.number.of.na <- results$NA.info.sample$multi.centre.vs.single.centre$multi.centre$total.number.of.na
## Sample NA
na.vector <- unlist(results$NA.info.sample)
highest.percent.missing.number <- max(na.vector[na.vector<100])
highest.percent.missing.name <- names((na.vector[na.vector == highest.percent.missing.number]))
## Variable NA
number.variable.na <- max(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na)
percent.variable.na <- results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$percentage[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na]
name.variable.na <- row.names( results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na,] )
gcs.na <- (results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre) == "ed_gcs_sum",])
sbp.na <- (results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre) == "ed_sbp_value",])
## Development and validation
high.low.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "high.volume"]
metro.non.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "metropolitan"]
multi.single.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "multi.centre"]
max.imp <- max(results$original.stats$Total.imputations)
best.validation <- results$original.stats[results$original.stats$Validation.mistriage.median == min(results$original.stats$Validation.mistriage.median),]
## Comparison
best.transfer <- results$original.stats[results$original.stats$Transfer.mistriage.median == min(results$original.stats$Transfer.mistriage.median),]
worst.transfer <- results$original.stats[results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median == max(results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median),]

## Table setup
# Table 1 = Sample characteristics table
#
# Table 2 = result.tables, cropped to only show validation
table.2 <- lapply(result.tables.data.frame, function(x) x[1:3,])
table.2 <- lapply(table.2, function(result) {
           kable(result, format = "markdown")
           })
# Table 3 = Cropped to only show transfer
table.3 <- lapply(result.tables.data.frame, function(x) x[4:6,])
table.3 <- lapply(table.3, function(result) {
           kable(result, format = "markdown")
           })
# Table 4 = Cropped to only show transfer differance
table.4 <- lapply(result.tables.data.frame, function(x) x[7:9,])
table.4 <- lapply(table.4, function(result) {
           kable(result, format = "markdown")
           })
```
# Introduction
Trauma results in millions of deaths annually across the globe, and road traffic injuries are among the top 10 leading causes of death worldwide (1, 2). Each year 9% of the world’s deaths are because of trauma, and predictions indicate that this number is likely to increase (3).

@@

Table 2 shows model validation performance. The sample with the lowest mistriage was the `r best.validation$Sample.name` sample with a median mistriage rate of `r best.validation$Validation.mistriage.median`. Performance in terms of under and overtriage for the same model was `r best.validation$Validation.undertriage.median`, and `r best.validation$Validation.overtriage.median` respectivly. Across all samples model validation performance in terms of mistriage ranged from `r min(results$original.stats$Validation.mistriage.median)` to `r max(results$original.stats$Validation.mistriage.median)`.

@@

## Comparison
Model performance after transfer was determined for each model being transferred to the other sample in the data set in all data sets (Table 3). When transferred, the model with the lowest mistriage rate was the `r best.transfer$Sample.name` model with a median mistriage of `r best.transfer$Transfer.mistriage.median`.

@@

The highest mistriage when compared to the reciveing sample validation model performance was found in the `r worst.transfer$Sample.name` sample, with a median mistriage difference of `r worst.transfer$Transferred.mistriage.minus.buddy.local.mistriage.median`, meaning this model performed worse when transferred to the other sample in the same data set.. In clinical terms, this model transfer means that among 100 trauma patients, `r abs(worst.transfer$Transferred.mistriage.minus.buddy.local.mistriage.median) * 100` more patients would be wrongly classified as major or minor trauma.

@@

# Discussion (Needs update with code snippets) 
This study aimed to assess how transfers of clinical prediction models for early trauma care between different contexts within a single health system affect mistriage rates. The most notable effects on model performance following model transfer were seen after transferring the metropolitan model. Mistriage increased by ... when using the metropolitan model in a non-metropolitan setting. Mainly contributing to this increase in mistriage was the marked increase in overtriage when performing this model transfer. For this particular transfer 95% UI ranged from ... to ..., indicating that our findings are compatible with a -0.055 decrease to 0.630 increase in mistriage. The negative 95% UI of ... would signifiy an improvement in model performance. The higher 95% UI of ... would mean a marked increase in model mistriage, compared to the point estimate of ....

>>>>

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
## LOAD FUNCTIONS, ENVIROMENT AND TABLES
source("functions/WorkTableCreator.R")
## Original results and UI tables
results <- readRDS("output/original.results.Rds")
result.tables <- readRDS("result.tables.Rds")
result.tables.data.frame <- readRDS("result.tables.data.frame.Rds")
## Create table for ease of data retrival
results.all.data <- WorkTableCreator(result.tables.data.frame)
## Sample characteristics table
# table.one <-

## RESULTS
## Characteristics paragraph
  ## Total patients and NA
  total.number.of.patients <- nrow(results$data.sets.before.imputations$multi.centre.vs.single.centre$multi.centre)
  total.number.of.na <- results$NA.info.sample$multi.centre.vs.single.centre$multi.centre$total.number.of.na
  ## Sample NA
  na.vector <- unlist(results$NA.info.sample)
  names(na.vector) <- c("high volume", "high volume", "low volume", "low volume", "metropolitan", "metropolitan", "non metropolitan", "non metropolitan", "multi centre", "multi centre", "single centre", "single centre")
  highest.percent.missing.number <- max(na.vector[na.vector<100])
  highest.percent.missing.name <- names((na.vector[na.vector == highest.percent.missing.number]))
  ## Variable NA
  number.variable.na <- max(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na)
  percent.variable.na <- results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$percentage[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na]
  name.variable.na <- row.names( results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na,] )
  gcs.na <- (results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre) == "ed_gcs_sum",])
  sbp.na <- (results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre) == "ed_sbp_value",])
## Development and validation
  ## Imputation data
  high.low.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "high.volume"]
  metro.non.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "metropolitan"]
  multi.single.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "multi.centre"]
  max.imp <- max(results$original.stats$Total.imputations)
  ## Validation data
  sorted.validation.mistriage <- sort(results.all.data[row.names(results.all.data) == "Validation.mistriage",], decreasing = FALSE)
  lowest.val.mistriage <- sorted.validation.mistriage[1]
  val.undertriage <- results.all.data["Validation.undertriage", colnames(lowest.val.mistriage)]
  val.overtriage <- results.all.data["Validation.overtriage", colnames(lowest.val.mistriage)]
  highest.val.mistriage <- sorted.validation.mistriage[6]
## Comparison
  ## Transfer data
  sorted.transfer.mistriage <- sort(results.all.data[row.names(results.all.data) == "Transfer.mistriage",], decreasing = FALSE)
  lowest.tran.mistriage <- sorted.transfer.mistriage[1]
  highest.tran.mistriage <- sorted.transfer.mistriage[6]
  ## Comparison data
  sorted.comp.mistriage <- sort(results.all.data[row.names(results.all.data) == "Transferred.mistriage.minus.buddy.local.mistriage",], decreasing = FALSE)
  highest.comp.mistriage <- sorted.comp.mistriage[6]
  worst.transfer <- results$original.stats[results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median == max(results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median),]
## DISCUSSION
  ## First paragraph
  UI.interval <- sub("\\).*", "", sub(".*\\(", "", format(highest.comp.mistriage)))
  UI.top.bot.list <- strsplit(UI.interval, split = " - ")
  UI.top.bot <- unlist(UI.top.bot.list)
## Table setup
  # Table 1 = Sample characteristics table
  #
  # Table 2 = result.tables, cropped to only show validation
  table.2 <- lapply(result.tables.data.frame, function(x) x[1:3,])
  table.2 <- lapply(table.2, function(result) {
             kable(result, format = "markdown")
             })
  # Table 3 = Cropped to only show transfer
  table.3 <- lapply(result.tables.data.frame, function(x) x[4:6,])
  table.3 <- lapply(table.3, function(result) {
             kable(result, format = "markdown")
             })
  # Table 4 = Cropped to only show transfer differance
  table.4 <- lapply(result.tables.data.frame, function(x) x[7:9,])
  table.4 <- lapply(table.4, function(result) {
             kable(result, format = "markdown")
             })
```
# Introduction
Trauma results in millions of deaths annually across the globe, and road traffic injuries are among the top 10 leading causes of death worldwide (1, 2). Each year 9% of the world’s deaths are because of trauma, and predictions indicate that this number is likely to increase (3).

@@

Table 2 shows model validation performance. The model with the lowest validation mistriage rate was the `r colnames(lowest.val.mistriage)` model with a median mistriage rate with 95% UI of `r lowest.val.mistriage`. Performance in terms of undertriage and overtriage rate for the same model was `r val.undertriage`, and `r val.overtriage` respectively. Worst validation performance i.e. highest mistriage rate was found in the `r colnames(highest.val.mistriage)` sample, with a model median mistriage rate of `r highest.val.mistriage`.

@@

## Comparison
Model performance after transfer was determined for each model being transferred to the other sample in the data set, in all data sets (Table 3). When transferred, the model with the lowest mistriage rate was the `r colnames(lowest.tran.mistriage)` model with a median mistriage rate of `r lowest.tran.mistriage`. The model with the highest mistriage rate after transfer was the `r colnames(highest.tran.mistriage)` with a median mistriage rate of `r highest.tran.mistriage`

@@

The highest mistriage rate when compared to the reciveing sample validation model performance was found in the `r colnames(highest.comp.mistriage)` model, with a median mistriage rate difference of `r highest.comp.mistriage`, meaning this model performed worse when transferred to the other sample in the same data set. In clinical terms, this model transfer means that among 100 trauma patients, `r abs(worst.transfer$Transferred.mistriage.minus.buddy.local.mistriage.median) * 100` more patients would be wrongly classified as major or minor trauma.

@@

# Discussion
This study aimed to assess how transfers of clinical prediction models for early trauma care between different contexts within a single health system affect mistriage rates. The most notable effects on model performance following model transfer were seen after transferring the `r colnames(highest.comp.mistriage)` model. The mistriage rate increased by `r substr(format(highest.comp.mistriage), 1, 5)` when using the `r colnames(highest.comp.mistriage)` model in the other sample in the same data set. Mainly contributing to this increase in mistriage was the marked increase in overtriage when performing this model transfer. For this transfer the 95% UI ranged from `r UI.top.bot[1]` to `r UI.top.bot[2]`, indicating that our findings are compatible with a `r UI.top.bot[1]` decrease to a `r UI.top.bot[2]` increase in mistriage. The negative 95% UI of `r UI.top.bot[1]` would signifiy an improvement in model performance. The higher 95% UI of `r UI.top.bot[2]` would mean a marked increase in model mistriage, compared to the point estimate of `r substr(format(highest.comp.mistriage), 1, 5)`.
